---
title: "p8105_hw1_hc3671"
author: "Barry"
date: "2025-09-15"
output: github_document
---

Loading package and dataset

```{r}
library(moderndive)
data("early_january_weather")
```

# Problem 1

**The description of data set:**

This data set records the weather condition in EWR from 1st to fifteenth of January in 2013. The weather condition includes variables like`r names(early_january_weather)[c(6,7,8,9,10,11,12,13,14,15)]` which refers to temperature, dew point, humidity, wind direction,wind speed, wind gust, precipitation, pressure, visibility and record times.\
This data set has `r ncol(early_january_weather)` columns and `r nrow(early_january_weather)` row.    
The mean temperature is `r mean(early_january_weather$temp)`.

Make a plot of temperature and time_hour

```{r}
library(ggplot2)

weather_plot <- ggplot(early_january_weather, aes(x = time_hour, y = temp, color = humid)) +
  geom_point() +
  labs(title = "Temperature vs Time (colored by humidity)", x = "Time", y = "Temperature (F)") +
  theme_minimal()

weather_plot
ggsave("scatterplot_of_weather.png", plot = weather_plot)
```

According to the plot, from the 1st to the 15th, the overall temperature shows an upward trend, with a regular daily cycle of lower temperatures in the morning and evening and higher temperatures around midday. At the same time, humidity is inversely related to temperature — in most cases, lower temperatures are associated with higher humidity.

# Problem 3.

First, we need to create a data frame includes different variables:

```{r}
library(tidyverse)
set.seed(123)
data_frame = tibble(
  sample = rnorm(10),
  is_positive = sample > 0,
  char_vec = sample(words, 10),
  fac_vec = factor(sample(
    c("A", "B", "C"), size = 10, replace = TRUE
  )),
)
```

Then, we are going to try take the mean of each variable in data_frame:

```{r}
mean(data_frame$sample)
mean(data_frame$is_positive)
#mean(data_frame$char_vec) is NA
#mean(data_frame$fac_vec) is NA
```

It shows that taking means works for the numeric and logistic(seen as 0 and 1), but not for the characters and factors.

```{r eval = FALSE}
as.numeric(data_frame$is_positive)
as.numeric(data_frame$char_vec)
as.numeric(data_frame$fac_vec)
```

